Analysis of the time-dependent response to Estradiol through ChIP-Seq data and the VULCAN package

### 2018-02-14 ChIP-seq_ER/rmarkdown.Rmd
Adjusted figures to make them easier it read

text(3,metabricmat["ESR1",3],label="ESR1",pos=4,cex=0.6,font=2,col="red3")

@@

text(3,newcoords,label=names(oricoords),pos=4,cex=0.6,font=2)
text(3,newcoords["ESR1"],label="ESR1",pos=4,cex=0.6,font=2,col="red3")

@@

text(3,newcoords,label=names(oricoords),pos=4,cex=0.6,font=2)

@@

text(3,newcoords,label=names(oricoords),pos=4,cex=0.6,font=2)

@@

newcoords<-setNames(seq(min(oricoords),min(oricoords)*1.2,length.out=length(oricoords)),names(oricoords))
text(3,newcoords,label=names(oricoords),pos=4,cex=0.6,font=2)

>>>>

text(3,metabricmat["ESR1",3],label="ESR1",pos=4,cex=1,font=2,col="red3")

@@

newcoords<-setNames(seq(min(oricoords)*0.7,max(oricoords),length.out=length(oricoords)),names(oricoords))
text(3,newcoords,label=names(oricoords),pos=4,cex=0.8,font=2)
text(3,newcoords["ESR1"],label="ESR1",pos=4,cex=1,font=2,col="red3")

@@

newcoords<-setNames(seq(min(oricoords),max(oricoords)*0.5,length.out=length(oricoords)),names(oricoords))
text(3,newcoords,label=names(oricoords),pos=4,cex=0.8,font=2)

@@

text(3,newcoords,label=names(oricoords),pos=4,cex=0.8,font=2)

@@

newcoords<-setNames(seq(min(oricoords)*0.7,min(oricoords)*1.4,length.out=length(oricoords)),names(oricoords))
text(3,newcoords,label=names(oricoords),pos=4,cex=0.8,font=2)
